MSDS6372Project1

### 2021-01-26 MSDS6372Project1.Rmd
change tibble to data frame
add three models for Objective 1

dim(train)

str(train)
str(CarData)
```

@@

```{r}

#### Objective 2 start without Log transformation - since there are so many categorical variables

>>>>

dim(train)
train = as.data.frame(train)
test = as.data.frame(test)
validate = as.data.frame(validate)
str(train)
str(CarData)
```

@@

```{r}
# Explore numerical variables
train %>% select(MSRP,Year,EngineHP,EngineCylinders,NumberOfDoors,HighwayMPG,CityMPG,Popularity)%>%ggpairs()
# Try Log transformation on MSRP see if it will improve correlations
train$logMSRP = log(train$MSRP)
train %>% select(logMSRP,Year,EngineHP,EngineCylinders,NumberOfDoors,HighwayMPG,CityMPG,Popularity)%>%ggpairs()
# It looks like logMSRP has increased correlation with Year but decreased correlation with EngineHP, EngineCylinders
# It's best to run LASSO and choose predictors on both with transformation and without Log transformation in order to identify which
# Model performs better
train = train[,-27]
#str(train)
library(glmnet)
# Since we want a easy to interperate model, we don't want to use predictor Make and Model that has too many levels in the model
train = train[,-(1:2)]
str(train)
#Dummy code categorical predictor variables
x <- model.matrix(MSRP~.,train)[,-1]
y <- log(train$MSRP)
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out)
# Look at coefficients
coef(cv.out, cv.out$lambda.min)
# Seems like LASSO has selected all predictors, only few levels within EngineFuel, TransmissionType, VehicleStyle got turned off
# Build model with predictors LASSO selected
log.model1 = lm(log(MSRP)~.,data=train)
par(mfrow=c(2,2))
plot(log.model1)
library(olsrr)
ols_plot_cooksd_bar(log.model1)
ols_plot_resid_stand(log.model1)
# Residual looks okay~
# Now try MSRP without log transformation

#Dummy code categorical predictor variables
x1 <- model.matrix(MSRP~.,train)[,-1]
y1 <- train$MSRP
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out1=cv.glmnet(x1,y1,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out1)
# Look at coefficients
coef(cv.out1, cv.out1$lambda.min)
# Again, all predictors are selected, only few levels are turned off
regular.model1 = lm(MSRP~.,data=train)
par(mfrow=c(2,2))
plot(regular.model1)
ols_plot_cooksd_bar(regular.model1)
ols_plot_resid_stand(regular.model1)

#############################################################################
# By comparison Constant variance looks a lot better with the log(MSRP)...###
# Since the assumption works best with this, next check with stepwise method to see what predictors will be selected
stepwise.model1 =lm(log(MSRP)~.,data=train)
ols_step_both_aic(stepwise.model1)
# By Using StepwiseAIC variable selection method, the following predictors are selected
# Year+EngineHP+Exotic+EngineFuelType+VehicleStyle+HighwayMPG+Hybrid+TransmissionType+EngineCylinders+Luxury+VehicleSize+FlexFuel+DrivenWheels+NumberOfDoors+Crossover+FactoryTuner+CityMPG+Popularity+N_A+Diesel
log.model2.step = lm(log(MSRP)~Year+EngineHP+Exotic+EngineFuelType+VehicleStyle+HighwayMPG+Hybrid+TransmissionType+EngineCylinders+Luxury+VehicleSize+FlexFuel+DrivenWheels+NumberOfDoors+Crossover+FactoryTuner+CityMPG+Popularity+N_A+Diesel,data=train)
par(mfrow=c(2,2))
plot(log.model2.step)
ols_plot_cooksd_bar(log.model2.step)
ols_plot_resid_stand(log.model2.step)

#compare test ASE results between stepwise model and 
test = test[,-(1:2)]
testMSRP = test$MSRP # GET real result 
test = test[,-13] # Delete MSRP from test 
# Calculate stepwise test ASE first
pred.test.step = predict(log.model2.step,test)
# exp values to return to original value
pred.test.step = exp(pred.test.step)
test_ASE_STEP = mean((testMSRP-pred.test.step)^2)
test_ASE_STEP #497620223

#Calculate LASSO test ASE
pred.test.lasso = predict(log.model1,test)
pred.test.lasso = exp(pred.test.lasso)
test_ASE_LASSO = mean((testMSRP-pred.test.lasso)^2)
test_ASE_LASSO #499722642

# By comparison, it seems LASSO performs a bit worse than StepwiseAIC selected predictors...
```

# Note: Rerun the code chunk for clean train/test/validate datasets - altered in Objective 1
#### Objective 2 start without Log transformation - since there are so many categorical variables
